---
title: "Cat Lovers"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

A survey asked respondents their name and number of cats. The instructions said to enter the number of cats as a numerical value.


```{r message=FALSE}

library(tidyverse)
library(DT)

cat_lovers <- read_csv("../data/cat-lovers.csv")

```


```{r echo=FALSE}
cat_lovers %>%
  datatable()
```


## Oh why won't you work?!

```{r}
cat_lovers %>%
  summarise(mean = mean(number_of_cats))
```

---

## Oh why won't you still work??!!

```{r}
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```

---

## Take a breath and look at your data

.question[
What is the type of the `number_of_cats` variable?
]

```{r}
glimpse(cat_lovers)
```

---

## Let's take another look

.small[
```{r echo=FALSE}
cat_lovers %>%
  datatable()
```
]

---

## Sometimes you need to babysit your respondents

```{r, ebal = FALSE}
cat_lovers %>%
  mutate(__) %>%
  summarise(mean_cats = mean(number_of_cats))
```

---

## Always you need to respect data types

```{r, eval = FALSE}
cat_lovers %>%
  mutate(__) %>%
  summarise(mean_cats = mean(number_of_cats))
```

---

## Now that we know what we're doing...

```{r}
cat_lovers <- cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    )
```
