---
title: "Lab NAME"
subtitle: "Data wrangling and visualization"
output: 
  tufte::tufte_html:
    tufte_variant: "envisioned"
    highlight: pygments
    css: lab.css
link-citations: yes
---

```{r include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

```{marginfigure}
For each exercise and on your own question you 
answer include any relevant output (tables, summary statistics, plots) in your 
answer. Doing this is easy! Just place any relevant R code in a code chunk, 
and hit Knit HTML.
```

Some define statistics as the field that focuses on turning information into
knowledge. The first step in that process is to summarize and describe the raw
information - the data. In this lab we explore the `pizzaplace` dataset from the [`gt` package](https://gt.rstudio.com/reference/pizzaplace.html).

>This dataset is unusual to say the least. It brings up more questions than answers. 


# Packages

In this lab we will work with the `tidyverse` package. We start by loading the package.

```{r}
library(tidyverse)

```

Note that these packages are also loaded in your R Markdown document.


# Load the data

The data frame we will be working with today is called `pizza` and it's in the `data` folder of this project.

```{r}
pizza <- read_csv("../data/pizza.csv")
```


This is synthetic dataset describing pizza sales for an imaginary pizza place. Each row is a pizza sold during 2015 - there are 32 different types of pizza in 4 different categories: classic, chicken, supreme, and veggie. 


`pizza` is a tidy **data frame**, with each row 
representing an **observation** and each column representing a **variable**.

To view the data, click on the name of the data frame in the Environment tab.

You can also take a quick peek at your data frame and view its dimensions 
with the `glimpse` function.

```{r glimpse}
glimpse(pizza)
```

The description of the variables, i.e. the **codebook**, is given below.

| Header                        |  Description
|:----------------|:--------------------------------
|`id`                           | The ID for the order, which consists of one or more pizzas at a give date and time
|`date`                         | A character representation of the order date, expressed in the ISO 8601 date format (YYYY-MM-DD)
|`time `                        | A character representation of the order time, expressed as a 24-hour time the ISO 8601 extended time format (hh:mm:ss)
|`name`                         | The short name for the pizza
|`size`                         | The size of the pizza, which can either be S, M, L, XL (rare!), or XXL (even rarer!); most pizzas are available in the S, M, and L sizes but exceptions apply
|`type`                         | The category or type of pizza, which can either be classic, chicken, supreme, or veggie
|`price`                        | The price of the pizza and the amount that it sold for (in USD)

The `pizza` data frame is a trove of information. Let's think about 
some questions we might want to answer with these data:

- Which pizza has the lowest price?
- Which major has the highest percentage of women?
- How do the distributions of median income compare across major categories?
- Do women tend to choose majors with lower or higher earnings?

In the next section we aim to answer these questions.

# Data wrangling and visualization

## Which pizza has the lowest price?

In order to answer this question all we need to do is sort the data. We use the
`arrange` function to do this, and sort it by the `price` variable. 
By default `arrange` sorts in ascending order, which is what we want here -- 
we're interested in the pizza with the *lowest* price.

```{r lowest-unemp}
pizza %>%
  arrange(price)
```

This gives us what we wanted, but not in an ideal form. Some of the variables are not 
that useful (e.g. `id`, `time`).

We can use the `select` function to choose which variables to display, and 
in which order:

```{marginfigure}
Note how easily we expanded our code with adding another step to our pipeline,
with the pipe operator: `%>%`.
```

```{r lowest-unemp-select}
pizza %>%
  arrange(price) %>%
  select(type, name, size, price)
```

Ok, this is looking better, but do we really need to see every **small, pepperoni order** to
understand that's the least expensive one. Not really! What do you think it's the second least expensive pizza?

We can address this problem by using `distinct` to avoid printing
duplicate rows (e.g. `name`). 

```{r}
pizza %>%
  arrange(price) %>%
  select(type, name, size, price) %>% 
  distinct(.keep_all = TRUE)

```

*note that this works because we did not select `id` in this commnand*


## Which pizza has the highest price?

To answer such a question we need to arrange the data in descending order. For 
example, if earlier we were interested in the major with the highest unemployment 
rate, we would use the following:

```{marginfigure}
The `desc` function specifies that we want `price` in descending order.
```

```{r}
pizza %>%
  arrange(desc(price)) %>%
  select(type, name, size, price) %>% 
  distinct(.keep_all = TRUE)
```


## Let

```{marginfigure}

Let's  pretend this pizza dataset is a recruitment datapull: 

```

